---
title: "HW6"
author: "Tongxi Yu"
date: "2023-12-03"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(purrr)
library(ggridges)
library(modelr)
```
# Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```
```{r}
lm(tmax ~ tmin + prcp, data = weather_df) |> 
  broom::tidy() |> 
  knitr::kable(digits = 3)
```
```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```



```{r}
boot_straps = 
  tibble(strap_number = 1:5000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(df = weather_df))
  )

boot_straps
```
```{r}
fit_lm = function(data) {
  lm(tmax ~ tmin + prcp, data = data)
}
```

Fit a linear regression model for each bootstrap sample

```{r}
bootstrap_results =
  boot_straps %>%
  mutate(
    lm_fit = map(strap_sample, fit_lm),
    r_squared = map_dbl(lm_fit, ~ broom::glance(.)$r.squared),
    beta_log_product = map_dbl(lm_fit, ~ log(coef(.)["tmin"] * coef(.)["prcp"]))
  )
```


```{r}
ggplot(bootstrap_results, aes(x = r_squared)) +
  geom_histogram(binwidth = 0.01, fill = "blue", color = "white") +
  labs(title = "Distribution of r^2 Estimates")
```
The r^2 estimations are close to normal distribution.
```{r}
ggplot(bootstrap_results, aes(x = beta_log_product)) +
  geom_histogram(binwidth = 0.1, fill = "green", color = "white") +
  labs(title = "Distribution of log(beta1 * beta2) Estimates")
```
log(beta1 * beta2) estimations are left-skewed
```{r}
conf_interval_r_squared = quantile(bootstrap_results$r_squared, c(0.025, 0.975))

conf_interval_beta_log_product = quantile(bootstrap_results$beta_log_product, c(0.025, 0.975), na.rm = TRUE)
```
```{r}
conf_interval_r_squared
conf_interval_beta_log_product
```

Problem 3

```{r}
bw_df <- read_csv("Data/birthweight.csv")
```
```{r}
summary(bw_df)
```
```{r}
missing_values <- colSums(is.na(bw_df))
print(missing_values)
```
```{r}
bw_df <- bw_df |>
  janitor::clean_names()|>
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  )

```
This dataset contains 4342 observations of 20 variables with no missing values. I'm trying to investigate the impact of several key factors on the weight of a newborn, as measured in grams (bwt). I chose to start with some factors might affect birthweight, including gestational age, mother's age, weight gain, and smoking during pregnancy.
```{r}
model1 <- lm(bwt ~ gaweeks + momage + wtgain + smoken, data = bw_df)
summary(model1)

library(ggplot2)
library(modelr)
library(dplyr)

bw_df <- bw_df |>
  modelr::add_predictions(model1,var = "pred") |>
  modelr::add_residuals(model1,var = "resid")

ggplot(bw_df, aes(x = pred, y = resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(title = "Residuals vs Fitted Values", x = "Fitted Values", y = "Residuals")
```
In summary, the model indicates that gestational age, mother's age, weight gain, and smoking during pregnancy are significant predictors of birth weight, and the overall model is statistically significant. The model explains about 22.82% of the variability in birth weight.
```{r}
model_length_gestational <- lm(bwt ~ blength + gaweeks, data = bw_df) 
```

```{r}
model_interactions <- lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = bw_df)
summary(model_interactions)

```

```{r}
cv_df=
  crossv_mc(bw_df,100)|>
   mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df=
  cv_df|>
  mutate(
    model1 = map(train,~lm(bwt ~ gaweeks + momage + wtgain + smoken, data = .x)),
    model_length_gestational  = map(train, ~lm(bwt ~ gaweeks + blength, data = .x)),
    model_interactions  = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x)))|>
  mutate(
    rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x,data = .y)),
    rmse_model_length_gestational = map2_dbl(model_length_gestational, test, ~rmse(model = .x,data = .y)),
    rmse_model_interactions = map2_dbl(model_interactions, test, ~rmse(model = .x,data = .y)))
```

```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse,fill = model)) + 
  geom_violin()+
  scale_fill_brewer(palette = "Pastel2") +
  labs(x = "Model", y = "RMSE", title = "Comparison of Model RMSEs") +
  theme_minimal()+
  theme(legend.position = "none")
```
The model using head circumference, length, sex, and all interactions (including the three-way interaction) between these has the lowest RMSE which indicates best model performance
